18th International Satisfiability Modulo Theories Competition (SMT-COMP 2023): Rules and Procedures

### 2023-04-12 rules/rules23.tex
SMT-COMP23 rules: updated dates and new submission time for system descriptions.

\begin{description}
\item[Mar~??] Deadline for new benchmark contributions.
\item[May~??] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[June~??] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[July~?] Deadline for final versions of solvers, including
  system descriptions.
\item[July~?] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[August~??] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2022 is part of the SMT Workshop~2022
(\url{http://smt-workshop.cs.uiowa.edu/2022/}),
which is affiliated with IJCAR~2022 (\url{https://easychair.org/smart-program/IJCAR2022/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state of the art in automated SMT problem
solving.

SMT-COMP 2022 will have seven tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
Services), and an experimental \prooftrack{} focused on a qualitative evaluation
of different proof formats, proof checkers and proof-producing solvers.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
%
We will recognize winners in all tracks but the \prooftrack{}.
%
They will be determined by the number of benchmarks solved (taking into account
the weighting detailed in Section~\ref{sec:scoring}); we will also recognize
solvers based on additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2022.
%

As in previous years, we have revised the rules slightly.  Some rule
changes in 2022 are designed to improve how logics are organized into
divisions. We have also added more divisions to the \mvaltrack and have defined a
new \prooftrack.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf System description must be submitted with preliminary
      solver.} \todo{what}
%
  \rationale{\todo{reason}}

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
supports solver configurations.  You can have at most one configuration
for each track (named after the track) and a default configuration used
for tracks without a track-specific configuration.
Moreover, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via the web form
at
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
short (1-2 pages, excluding references; plus 2 pages for proof format and proof
checker if the entrant is for the proof exhibition track) description of the system, which \textbf{must} explicitly
acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
\emph{derived} tool (see above).
In case of a \emph{wrapper} tool, it \textbf{must} also explicitly state
the exact version of each wrapped solver.
A system description \textbf{must} further include the following information:
\begin{itemize}[itemsep=0ex]
  \item a list of all (current) authors of the system and their present institutional
    affiliations,
  \item the basic SMT solving approach employed,
  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
    technical innovations by which a wrapper or derived tool expects to improve
    on the wrapped solvers or base solver,
  \item appropriate acknowledgment of tools other than SMT solvers called by
    the system (e.g., SAT solvers) that are not written by the authors of the
    submitted solver, and
  \item for participants of the \prooftrack{} a short description
    of their proof format of up to two extra pages.
\end{itemize}
A system description \emph{should} further include the following information
(unless there is a good reason otherwise):
\begin{itemize}[itemsep=0ex]
  \item details of any non-standard algorithmic techniques as well as
    references to relevant literature (by the authors or others), and
  \item a link to a website for the submitted tool.
\end{itemize}
System descriptions \textbf{must} be submitted \textbf{until the final solver
deadline}, and will be made publicly available on the competition website.
Organizers will check that they contain sufficient information
and may withdraw a system if its description is not sufficiently updated upon
request

@@

SMT-COMP entrants must be submitted via StarExec (solvers), or
communicated separately to the organisers for the \paralleltrack{} and
\cloudtrack{}, \emph{and}
the above web form (accompanying information) until the end of
{\bf June~18, 2022} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec or \paralleltrack{}
and \cloudtrack{}
will be accepted until the end of {\bf July~2, 2022} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2022.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2022/parallel-and-cloud-tracks.html}.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~15, 2022}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf June~18, 2022}.

@@

SMT-COMP 2022 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
\item \href{TODO}{Martin Bromberger}~-- TODO
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Martin TODO
%
Jochen is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.

>>>>

\begin{description}
\item[Mar~31] Deadline for new benchmark contributions.
\item[April~29] Final versions of competition tools (e.g., benchmark
  scrambler) are made available.  Benchmark libraries are frozen.
\item[May~13] Deadline for first versions of solvers (for all tracks),
  including information about which tracks and divisions are being
  entered, and magic numbers for benchmark scrambling.
\item[May~27] Deadline for final versions of solvers, including
  system descriptions.
\item[May~30] Opening value of NYSE Composite Index used to compute
  random seed for competition tools.
\item[July~5-6] SMT Workshop; end of competition, presentation of
  results.
\end{description}

@@

SMT-COMP~2023 is part of the SMT Workshop~2023
(\url{http://smt-workshop.cs.uiowa.edu/2023/}),
which is affiliated with CADE~29 (\url{https://easyconferences.eu/cade2023/}).
The SMT Workshop will include a block of time to present the results of the
competition.
%
Accordingly, researchers are highly encouraged to submit both new
benchmarks and new or improved solvers to raise the level of
competition and advance the state of the art in automated SMT problem
solving.

SMT-COMP 2023 will have seven tracks: the \maintrack (before 2019: Main Track),
the \inctrack (before 2019: Application Track), the \ucoretrack, the \mvaltrack,
the \paralleltrack{} and the \cloudtrack{} (both sponsered by Amazon Web
Services), and an experimental \prooftrack{} focused on a qualitative evaluation
of different proof formats, proof checkers and proof-producing solvers.
%
Within each track there are multiple divisions, where each division
uses benchmarks from a specific group of SMT-LIB logics.
%
We will recognize winners in all tracks but the \prooftrack{}.
%
They will be determined by the number of benchmarks solved (taking into account
the weighting detailed in Section~\ref{sec:scoring}); we will also recognize
solvers based on additional criteria.

The rest of this document, revised from the previous
version,\footnote{Earlier versions of this document include
  contributions from Clark Barrett, Roberto Bruttomesso, David Cok,
  Sylvain Conchon, David D{\'e}harbe, Morgan Deters, Alberto Griggio,
  Liana Hadarean,
  Matthias Heizmann, Antti Hyvarinen, Aina Niemetz, Albert Oliveras, Giles Reger, Aaron Stump,
  and Tjark Weber.}  describes the rules and competition procedures for
SMT-COMP~2023.
%

As in previous years, we have revised the rules slightly.  Some rule
changes in 2023 are designed to improve how logics are organized into
divisions. We have also added more divisions to the \mvaltrack and have defined a
new \prooftrack.
%
The principal changes from the previous competition rules are the following:
\begin{itemize}
  \item {\bf System descriptions.}  \emergencystretch.5cm The system description 
  for a participating solver must be submitted by the deadline for the preliminary 
  solver versions. In the case a system description contains not all necessary information,
  participants will be asked to submit an updated version of their 
  system description as part of the submission of the final version of their solver.
%
  \rationale{We need this time to check whether the system descriptions contain all
  necessary information and to give participants the chance to fix their system 
  descriptions if necessary.}

@@

\header{Participation in the Competition.}
%
For participation in SMT-COMP, a solver must be uploaded to StarExec
and made publicly available, or communicated separately to the
organisers for the \cloudtrack{} and \paralleltrack{}.  StarExec
supports solver configurations.  You can have at most one configuration
for each track (named after the track) and a default configuration used
for tracks without a track-specific configuration.
Moreover, the organizers must be informed of the solver's presence
\emph{and the tracks and divisions which it enters} via the web form
at \todo{Needs to be updated!}
\begin{center}
  \url{https://forms.gle/ewNQdFJbmQ12GxpX8}
\end{center}
For each track the submission must specify the logics which are
supported by the solver.  The solver will enter all divisions where it
supports at least one logic.  A submission \textbf{must} also include a
link to the \emph{system description} (see below) and a \emph{32-bit
  unsigned integer}.  These integer numbers, collected from all
submissions, are used to seed competition tools.

\header{System description.}
%
As part of the submission, SMT-COMP entrants are \textbf{required} to provide a
short (1-2 pages, excluding references; plus 2 pages for proof format and proof
checker if the entrant is for the proof exhibition track) description of the system, which \textbf{must} explicitly
acknowledge any solver it wraps or is based on in case of a \emph{wrapper} or
\emph{derived} tool (see above).
In case of a \emph{wrapper} tool, it \textbf{must} also explicitly state
the exact version of each wrapped solver.
A system description \textbf{must} further include the following information:
\begin{itemize}[itemsep=0ex]
  \item a list of all (current) authors of the system and their present institutional
    affiliations,
  \item the basic SMT solving approach employed,
  \item in case of a \emph{wrapper} or \emph{derived tool}: details of
    technical innovations by which a wrapper or derived tool expects to improve
    on the wrapped solvers or base solver,
  \item appropriate acknowledgment of tools other than SMT solvers called by
    the system (e.g., SAT solvers) that are not written by the authors of the
    submitted solver, and
  \item for participants of the \prooftrack{} a short description
    of their proof format of up to two extra pages.
\end{itemize}
A system description \emph{should} further include the following information
(unless there is a good reason otherwise):
\begin{itemize}[itemsep=0ex]
  \item details of any non-standard algorithmic techniques as well as
    references to relevant literature (by the authors or others), and
  \item a link to a website for the submitted tool.
\end{itemize}
System descriptions \textbf{must} be submitted \textbf{by the preliminary solver
submission deadline}, and will be made publicly available on the competition website.
Organizers will check that they contain sufficient information
and may withdraw a system if its description is not sufficiently updated upon
request. The updates must happen \textbf{by the final solver submission deadline}.

@@

SMT-COMP entrants must be submitted via StarExec (solvers), or
communicated separately to the organisers for the \paralleltrack{} and
\cloudtrack{}, \emph{and}
the above web form (accompanying information) until the end of
{\bf May~13, 2023} anywhere on earth.
After this date \emph{no new entrants} will be accepted.
However, updates to existing entrants on StarExec or \paralleltrack{}
and \cloudtrack{}
will be accepted until the end of {\bf May~27, 2023} anywhere on earth.

@@

\header{Dates of Competition.}
%
The bulk of the computation will take place during the weeks leading
up to SMT 2023.  Intermediate results will be regularly posted to the
SMT-COMP website as the competition runs.
%
The organizers reserve the right to prioritize certain competition
tracks or divisions to ensure their timely completion, and in
exceptional circumstances to complete divisions after the SMT
Workshop.

@@

The limits for \paralleltrack{} and \cloudtrack{} are available at
\url{https://smt-comp.github.io/2023/parallel-and-cloud-tracks.html}.

@@

\header{New benchmarks.}
The deadline for submission of new benchmarks was {\bf March~31, 2023}.
%
The organizers, in collaboration with the SMT-LIB maintainers, will be
checking and curating these until {\bf May~13, 2023}.

@@

SMT-COMP 2023 is organized under the direction of the SMT Steering
Committee. The organizing team is
%
\begin{itemize}
\setlength{\itemsep}{0pt}
\item \href{https://github.com/bobot}{Fran\c{c}ois Bobot}~-- CEA List, France (chair)
\item \href{https://www.mpi-inf.mpg.de/departments/automation-of-logic/people/martin-bromberger}{Martin Bromberger}~-- MPI-INF, Germany
\item \href{https://jochen-hoenicke.de/}{Jochen Hoenicke}~-- Certora, Germany
\end{itemize}
%
The competition chairs are responsible for policy and procedure decisions,
such as these rules, with input from the co-organizers.

@@

\header{Disclosure.}
Fran\c{c}ois is part of the developing team of the SMT solver COLIBRI~\cite{colibri}.
%
Martin is part of the developing team of the SMT solver
SPASS-SATT~\cite{spass-satt}.
%
Jochen is part of the developing team of the SMT solver
SMTInterpol~\cite{smtinterpol}.
